---
title: "Simulating Carbon Markets"
author: "Daphne Virlar"
date: "5/30/2019"
output: html_document
---


<style type="text/css">

h1.title {
  text-align: center;
  font-family: "Times New Roman", Times, serif;
}
h4.author {
  font-family: "Times New Roman", Times, serif;
  text-align: center;
  font-size: 26px;
}
h4.date { 
  font-family: "Times New Roman", Times, serif;
  text-align: center;
}

body {
font-family: "Times New Roman", Times, serif;
font-size: 20px;
}
</style>



```{r setup, include=FALSE}

library(tidyverse)
#library(gridExtra)    # don't know if we'll use
#library(cowplot)      # don't know if we'll use
#library(grid) # to use grobs         # don't know if we'll use
library(extrafont) # to change font in graphs 
#    font_import() # import fonts
 #   fonts() # check fonts that are now loaded 
library(kableExtra)


###########################################################################################################
    # Load data
carbon <- read.csv("HW4Data.csv")

```



##Problem 1:
1. Write down a plausible functional form for the marginal cost of abatement for sectors A, B, C, and D. 
2. How well do the models fit? What are the parameters? (Kable Table).
3. Create a plot of the estimated marginal abatement cost functions in all four sectors. **This needs to go into memo**
```{r, include= FALSE}
# Notes on abatement costs

# Abatement cost is the cost of reducing environmental negatives such as pollution. 

# Although marginal abatement costs can be negative, such as when the low carbon option is cheaper than the business-as-usual option, marginal abatement costs often rise steeply as more pollution is reduced.

############################################################################################################

                           # Create Linear Models for Marginal Abatement Cost Curve

#Create a linear model that explains how marginal cost is influenced by abatement
    #Creating a linear model to give you the equation of the line.

# Sector A
abatement_a <- lm(carbon$MC_A ~ carbon$Abatement)
summary(abatement_a)
      # intercept = -8.6445
      # slope = 0.5768
      # R^2 = 0.904
  intercept_a <- abatement_a$coefficients[1]
  slope_a <- abatement_a$coefficients[2]
  r_a <- 0.904
  
# Sector B
abatement_b <- lm(carbon$MC_B ~ carbon$Abatement)
summary(abatement_b)
      # intercept = 9.31770
      # slope = 0.19874
      # R^2 = 0.5355
  intercept_b <- abatement_b$coefficients[1]
  slope_b <- abatement_b$coefficients[2]
  r_b <- 0.5355
  
# Sector C
abatement_c <- lm(carbon$MC_C ~ carbon$Abatement)
summary(abatement_c)
      # intercept = -11.655
      # slope = 0.78383
      # R^2 = 0.8752
  intercept_c <- abatement_c$coefficients[1]
  slope_c <- abatement_c$coefficients[2]
  r_c <- 0.8752
  
# Sector D
abatement_d <- lm(carbon$MC_D ~ carbon$Abatement)
summary(abatement_d)
      # intercept = 9.68751
      # slope = 0.25993
      # R^2 = 0.5434
  intercept_d <- abatement_d$coefficients[1]
  slope_d <- abatement_d$coefficients[2]
  r_d <- 0.5434
    

############################################################################################################

                               # Write functions for Marginal Abatement Cost Curve

# Sector A
curve_a <- function(x){
  intercept_a + slope_a*x
}

  
# Sector B
curve_b <- function(x){
  intercept_b + slope_b*x
}

  
# Sector C
curve_c <- function(x){
  intercept_c + slope_c*x
}


# Sector D
curve_d <- function(x){
  intercept_d + slope_d*x
}

```


------ insert section including all the linear regessions written out ---------



```{r, echo=FALSE, message=TRUE}
# create a kable table listing the parameters of each regression, and the R^2 value. Rows = each sector

# create a new data frame
kable_data <- data.frame("Sector" = c("A", "B", "C", "D"),
                         "Intercept" = round(c(intercept_a, intercept_b, intercept_c, intercept_d), 2),
                         "Slope" = round(c(slope_a, slope_b, slope_c, slope_d), 2),
                         "R-Squared" = round(c(r_a, r_b, r_c, r_d), 2))

sector_table <- kable(kable_data,
                      col.names = c("Sector", "Intercept", "Slope", "R-Squared" )) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "bordered"))
sector_table
```


```{r, include=FALSE, echo=TRUE}
# I went way overboard originally with how I created the graphs. This time, I'm essentially copying what I did in the Gas Tax assignment. That is, 
        # graphing multiple functions on one graph, 
        # assigning a name to each of them, 
        # and color coding them

ggplot(data.frame(x = c(0, 350))) + # setting a data frame basically allows for R to evaluating the function along those values
  stat_function(fun = curve_a, aes(color = "A")) +
  stat_function(fun = curve_b, aes(color = "B")) +
  stat_function(fun = curve_c, aes(color = "C")) +
  stat_function(fun = curve_d, aes(color = "D")) +
                             # color is set to the name so that it's easier to fix                                                        the legend later on
  ###
  # without setting the axes, nothing shows up.
  scale_y_continuous(limits= c(-15,120), expand = c(0,0)) +
  scale_x_continuous(limits= c(0, 350), expand = c(0,0)) + 
            # x axis is set to 350 because sector D emits up to 300 tons of carbon. So that's at least how               much they'll have to abate
  ###
  labs(fill = "", color = "Sectors") + # this changes the title of the legend
  xlab("\n Carbon Abatement (ton)") + 
  ylab("Carbon Value \n($/ton) \n") + # should this just be marginal cost? 
  ggtitle("Marginal Cost of Abatement\n") + # this needs to be centered
  ###
  theme(plot.title = element_text(hjust = 0.5), # centers the title
        axis.title.y = element_text(angle=0, hjust = 0.5, vjust = 0.5)) # Rotates y lab 90 deg, and centers



```



##Problem 2
1. Derive demand curve for each sector
2. Plot the demand curves
3. Which sector is willing to pay the most? (This will be the one with the highest intercept)
```{r}
############################################################################################################

                               # Write functions for Each Sectors Demand Curve

# Find marginal abatement costs for each sector. This will be the new intercept values for 
# plugging into y = mx + b. 

y_interceptA <- curve_a(180)
y_interceptB <- curve_b(200)
y_interceptC <- curve_c(220)
y_interceptD <- curve_d(300)




# Create Equations by Sector

demand_a <- function(x){
  # intercept  +     slope * x
  y_interceptA + (-y_interceptA / 180)*x
}


demand_b <- function(x){
  # intercept  +     slope * x
  y_interceptB + (-y_interceptB / 200)*x
}


demand_c <- function(x){
  # intercept  +     slope * x
  y_interceptC + (-y_interceptC / 220)*x
}

demand_d <- function(x){
  # intercept  +     slope * x
  y_interceptD + (-y_interceptD / 300)*x
}




```


```{r}
ggplot(data.frame(x = c(0, 350))) + # setting a data frame basically allows for R to evaluating the function along those values
  stat_function(fun = demand_a, aes(color = "A")) +
  stat_function(fun = demand_b, aes(color = "B")) +
  stat_function(fun = demand_c, aes(color = "C")) +
  stat_function(fun = demand_d, aes(color = "D")) +
                             # color is set to the name so that it's easier to fix                                                        the legend later on
  ###
  # without setting the axes, nothing shows up.
  scale_y_continuous(limits= c(0, 170), expand = c(0,0)) +
  scale_x_continuous(limits= c(0, 300), expand = c(0,0)) + 

  ###
  labs(fill = "", color = "Sectors") + # this changes the title of the legend
  xlab("\n Carbon Pollution (ton)") + 
  ylab("Carbon Value \n($/ton) \n") + # should this just be marginal cost? 
  ggtitle("Marginal Cost of Pollution\n") + # this needs to be centered
  ###
  theme(plot.title = element_text(hjust = 0.5), # centers the title
        axis.title.y = element_text(angle=0, hjust = 0.5, vjust = 0.5)) # Rotates y lab 90 deg, and centers


```


## Part 3
```{r}
# Part A, Section 1
  # The total cost of meeting the target in country X
      # Emissions cut by 100 tons

# We are integrating because our "curve_X" functions are the MARGINAL abatement cost. Any marginal curve is the DERIVATIVE of a total curve. Therefore, to find the TOTAL emissions, we need to integrate under the curve in order to find the total price of abating 100 tons of carbon.
cost_A = integrate(curve_a, 0, 100)
cost_B = integrate(curve_b, 0, 100)
cost_C = integrate(curve_c, 0, 100)
total_cost = cost_A$value + cost_B$value + cost_C$value  


```



```{r, echo=FALSE, message=TRUE}
# Part A, Section 2
  # The cost to each sector

cb_data <- data.frame("Sectors" = c("A", "B", "C", "Total"),
                      "Abating" = c(round(cost_A$value, 2),
                                            round(cost_B$value, 2),
                                            round(cost_C$value, 2),
                                            round(cost_A$value + cost_B$value + cost_C$value, 2)))


cb_table <- cb_data %>% 
  kable(col.names = c("Sectors", "Cost of Abating"),
        align = rep('c', 5)) %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), position = "center", full_width = F)

cb_table

```

#####The above kable table indicates the cost of abating by sector, along with the total cost for Country X. The total benefit of polluting, theoretically, should be the same for each sector.

```{r}

# Sector A
  intercept_a <- abatement_a$coefficients[1]
  slope_a <- abatement_a$coefficients[2]
  
# Sector B
  intercept_b <- abatement_b$coefficients[1]
  slope_b <- abatement_b$coefficients[2]

  
# Sector C
  intercept_c <- abatement_c$coefficients[1]
  slope_c <- abatement_c$coefficients[2]
  
# Sector D
  intercept_d <- abatement_d$coefficients[1]
  slope_d <- abatement_d$coefficients[2]


# Aggregate Slope
Slope_ag =(1/slope_a)+(1/slope_b)+(1/slope_c)

# Aggregate Intercept 
Intercept_ag = (-(intercept_a/slope_a)-(intercept_b/slope_b)-(intercept_c/slope_c))


# For 3-A-3, we are finding the AREA UNDER THE CURVE. We need to find the tax on carbon first. This will be the y-intercept for where x=300 on the aggregate supply curve. Then, we need to integrate from 0 to 300. This integration is what gives us the tax revenue generated.

```

