---
title: "Simulating Carbon Markets"
author: "Daphne Virlar"
date: "5/30/2019"
output: html_document
---


<style type="text/css">

h1.title {
  text-align: center;
  font-family: "Times New Roman", Times, serif;
}
h4.author {
  font-family: "Times New Roman", Times, serif;
  text-align: center;
  font-size: 26px;
}
h4.date { 
  font-family: "Times New Roman", Times, serif;
  text-align: center;
}

body {
font-family: "Times New Roman", Times, serif;
font-size: 20px;
}
</style>



```{r setup, include=FALSE}

library(tidyverse)
#library(gridExtra)
#library(cowplot)
#library(grid) # to use grobs
library(extrafont) # to change font in graphs 
#    font_import() # import fonts
 #   fonts() # check fonts that are now loaded 


###########################################################################################################
    # Load data
carbon <- read.csv("HW4Data.csv")

```



##Problem 1:
1. Write down a plausible functional form for the marginal cost of abatement for sectors A, B, C, and D. 
2. How well do the models fit? What are the parameters? (Kable Table).
3. Create a plot of the estimated marginal abatement cost functions in all four sectors. **This needs to go into memo**
```{r}
# Notes on abatement costs

# Abatement cost is the cost of reducing environmental negatives such as pollution. 

# Although marginal abatement costs can be negative, such as when the low carbon option is cheaper than the business-as-usual option, marginal abatement costs often rise steeply as more pollution is reduced.

############################################################################################################

                           # Create Linear Models for Marginal Abatement Cost Curve

#Create a linear model that explains how marginal cost is influenced by abatement
    #Creating a linear model to give you the equation of the line.

# Sector A
abatement_a <- lm(carbon$MC_A ~ carbon$Abatement)
summary(abatement_a)
      # intercept = -8.6445
      # slope = 0.5768
      # R^2 = 0.904
  intercept_a <- abatement_a$coefficients[1]
  slope_a <- abatement_a$coefficients[2]
  
  
# Sector B
abatement_b <- lm(carbon$MC_B ~ carbon$Abatement)
summary(abatement_b)
      # intercept = 9.31770
      # slope = 0.19874
      # R^2 = 0.566
  intercept_b <- abatement_b$coefficients[1]
  slope_b <- abatement_b$coefficients[2]

# Sector C
abatement_c <- lm(carbon$MC_C ~ carbon$Abatement)
summary(abatement_c)
      # intercept = -11.655
      # slope = 0.78383
      # R^2 = 0.8752
  intercept_c <- abatement_c$coefficients[1]
  slope_c <- abatement_c$coefficients[2]

  
# Sector D
abatement_d <- lm(carbon$MC_D ~ carbon$Abatement)
summary(abatement_d)
      # intercept = 9.68751
      # slope = 0.25993
      # R^2 = 0.5434
  intercept_d <- abatement_d$coefficients[1]
  slope_d <- abatement_d$coefficients[2]
    

############################################################################################################

                               # Write functions for Marginal Abatement Cost Curve

# Sector A
curve_a <- function(x){
  intercept_a + slope_a*x
}

  
# Sector B
curve_b <- function(x){
  intercept_b + slope_b*x
}

  
# Sector C
curve_c <- function(x){
  intercept_c + slope_c*x
}


# Sector D
curve_d <- function(x){
  intercept_d + slope_d*x
}

```


------ insert section including all the linear regessions written out ---------



```{r}
# create a kable table listing the parameters of each regression, and the R^2 value. Rows = each sector

```



```{r}
# Create all the plots, and arrange them in a single frame
      # when creating the plots, don't necessarily need to graph by function... Sam said we could draw the         lines on. Can you integrate this?
```



##Problem 2
1. Derive demand curve for each sector
2. Plot the demand curves
3. Which sector is willing to pay the most? (This will be the one with the highest intercept)
```{r}

```

